Scientific Reasoning with LLMs

### 2024-10-29 docs/proposal/main.tex
RQs

\paragraph{RQ2}
We plan to

\paragraph{RQ3}
In order to distill the knowledge from the model fine-tuned in previous steps, we plan to do the model distillation with Chain-of-Thought Prompting for Reasoning approach. Following techniques described in \cite{magister2022teaching} \cite{wei2022chain}, the student model will be fine-tuned using these CoT responses to produce intermediate reasoning steps. At the same time, the teacher model generates multiple CoT responses, and the student learns from the aggregate (self-consistent) reasoning paths. The described approach can help the student model avoid common mistakes and output more consistent answers.

>>>>

\paragraph{RQ2}
We plan to use Soft Prompting on the LLM used to guide it towards better reasoning.

\paragraph{RQ3}
In order to distill the knowledge from the obtained model previous steps, we plan to do the model distillation with Chain-of-Thought Prompting for Reasoning approach. Following techniques described in \cite{magister2022teaching} \cite{wei2022chain}, the student model will be fine-tuned using these CoT responses to produce intermediate reasoning steps. At the same time, the teacher model generates multiple CoT responses, and the student learns from the aggregate (self-consistent) reasoning paths. The described approach can help the student model avoid common mistakes and output more consistent answers.
